Metric Spaces with Expensive Distances

### 2019-03-31 paper/esa_draft.tex
Add McGill original table

% uncomment for Arxiv
\usepackage{arxiv}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
% END uncomment for Arxiv

\usepackage{booktabs}       % professional-quality tables
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{mathbbol}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{url}
\usepackage{floatflt}
\usepackage{mathptmx}
\usepackage{epsfig}
\usepackage{wrapfig}
\usepackage{color}

@@

% uncomment for Arxiv
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{note}[theorem]{Note}
% END uncomment for Arxiv

@@

% uncomment for Arxiv
\author{Michael Kerber\\
Graz University of Technology \\
Institut für Geometrie \\
Kopernikusgasse 24, 8010 Graz, Austria \\
\And
Arnur Nigmetov\\
Graz University of Technology \\
Institut für Geometrie \\
Kopernikusgasse 24, 8010 Graz, Austria \\
}
%\\
%kerber@tugraz.at\\
%Supported by Austrian Science Fund (FWF) grant number P 29984-N35
%\And

%Arnur Nigmetov
%Graz University of Technology\\
%Institut fuer Geometrie\\
%Kopernikusgasse 24\\
%8010 Graz\\
%Austria\\
%nigmetov@tugraz.at}

@@

\bibliography{bib}
\bibliographystyle{plainnat}

>>>>

\usepackage{arxiv}

\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{mathbbol}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{url}
\usepackage{floatflt}
\usepackage{mathptmx}
\usepackage{epsfig}
\usepackage{wrapfig}
\usepackage{color}

@@

%\newtheorem{theorem}{Theorem}
%\newtheorem{lemma}[theorem]{Lemma}
%\newtheorem{proposition}[theorem]{Proposition}
%\newtheorem{corollary}[theorem]{Corollary}
%\newtheorem{definition}[theorem]{Definition}
%\newtheorem{remark}[theorem]{Remark}
%\newtheorem{note}[theorem]{Note}

@@

% uncomment for Arxiv
\author{Michael Kerber\\
Graz University of Technology\\
Institut fuer Geometrie\\
Kopernikusgasse 24\\
8010 Graz\\
Austria\\
kerber@tugraz.at\\
Supported by Austrian Science Fund (FWF) grant number P 29984-N35
\And

Arnur Nigmetov
Graz University of Technology\\
Institut fuer Geometrie\\
Kopernikusgasse 24\\
8010 Graz\\
Austria\\
nigmetov@tugraz.at}

@@

\bibliography{bib}
\bibliographystyle{plain}
